---
output: rmarkdown::github_document
---

# randquotes


## Description

This package connects to the site <http://quotesondesign.com/> that uses the WordPress JSON REST API to provide a way for you to grab quotes.

## Overview

This package contains the following function:
`randquote()` that fetches a random quote and returns a dataframe along with the author name and link to the quote.

## Installation

```{r eval=FALSE}
devtools::install_github("amrrs/randquotes")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Note

This package fetches data from API hence an active internet connection is required for this package to function.

## Current Version

```{r message=FALSE, warning=FALSE, error=FALSE}
library(randquotes)

# current verison
packageVersion("randquotes")

```

## Usage


```{r}
library(randquotes)

randquote()
```

## Courtesy

This R package is powered by [Quotes on Design API](https://quotesondesign.com/api-v4-0/)

## Contribution

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.