---
title: "Using the randquote package"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the randquote package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package connects to the site <http://quotesondesign.com/> that uses the WordPress JSON REST API to provide a way for you to grab quotes.

## Overview

This package contains the following function: `randquote()` that fetches a random quote and returns a dataframe along with the author name and link to the quote.

## Installation

The stable version of `randquotes` can be installed from CRAN:

```{r,eval=FALSE}
install.packages("randquotes")
```

And the development version can be installed from github:

```{r,eval=FALSE}
devtools::install_github("amrrs/randquotes")
```

### Note

This package fetches data from API hence an active internet connection is required for this package to function.

## Current Version

``` {r}
library(randquotes)

# current verison
packageVersion("randquotes")
```

## Usage

### Get Random Quote

```{r}
library(randquotes)

randquote()
```


### Get only the Quote

Sometimes you may not be interested in getting a dataframe that has ID
and link, so this function `randquote_simple()` outputs only the quote
with author name.

```{r}
library(randquotes)

cat(randquotes::randquote_simple())
```


